Envelope Estimation using Geometric Properties of a Discrete Real Signal

### 2021-08-25 Papers/01_Pulses_Envelope/Response to Reviewers.tex

% \bibliographystyle{elsarticle-num}
\begin{document}

\title{Response to Reviewers}

\maketitle

\section{Reviewer #4}
The comments have been well address by the authors. The manuscript has also been well revised based on comments.

\section{Reviewer #8} The revised manuscript was much better than the original one. According to previous comments, the writing style of this revised version was largely improved, and some key concepts were much clearer compared with the original one. Most of the previous comments were well addressed. This reviewer just has several minor comments.

\subsection{The term 'benchmarking' always refers to the 'true value', or some 'gold standard' method that best estimates the true value. In the revised manuscript, section 7.2, the authors described two methods, which one was used as the 'benchmarking' for calculating the results listed in Table 1?}

Only one method is described in section 7.2, the reference envelope. We changed the text to make this clear (line 320), and better defined this method, that was formalized in an equation (line 325). We also made clear that this is the method used as reference in Table 1 (line 331).

\subsection{What's the main drawback of POST-processing(filtering) of Hilbert transform? Although the Table 1 has already shown the error of this method. The reviewer suggests the author give an intuitive explanation. For example, around Figure.4, can we say the POST- filtering of Hilbert transform mis-estimated the envelope in magnitude?}

We can affirm that post filtering the result of the Hilbert transform will generally underestimate the envelope. This can be better understood in the frequency domain: By low pass filtering in the time domain, we are essentially zeroing frequency bins in the frequency domain above a certain frequency threshold and lowering the total energy of the transform result.

This procedure isn't intrinsically detrimental, however, in the sense that if the original result of the transform is smooth, those frequencies would already be absent, and the corresponding bins would be zero from the beginning. Filtering wouldn't change the original output of the transform.

We changed the text to make this more intuitive (line 92).

\subsection{The Figure.15 should be moved before Figure.13, since this Figure was mentioned earlier (line 294) than Figure.13 and Figure.14.}
Despite being mentioned earlier (line 301 of the revised manuscript), Fig. 15 is better understood after the description of the envelope extraction algorithms it exemplifies, presented after Figs 13 and 14, in Section "7.3. Comparison with traditional algorithms". To avoid a major reorganization of the text, we therefore indicated in its first mention (line 301) that the figure is to be found in section "7.3. Comparison with traditional algorithms".

\subsection{Did the proposed algorithm require the known carrier c as a priori knowledge? This algorithm may not need this information. However, the author should clarify that in the manuscript.}

A priori knowledge of the carrier c is not required. We feel that the misunderstanding in this regard is introduced shortly after the definition of the vectors c, e and w in equation 1, in the subsequent paragraph. We therefore reworked this paragraph to make this more apparent (line 115).

\subsection{Line 216, did the author mean 'vk,y->0 => rk -> infinite'?}

That was indeed what we intended, and we are sorry for the overlook. We corrected this error in line 223 of the revised version.

\section{Reviewer #9} The authors have put great effort to revise the manuscript and addressed all comments from other reviewers. I don't have other comments to add.

### 2021-08-25 Papers/01_Pulses_Envelope/00ElsevierPulsesEnvelope.tex
incorporated suggestions review 2

For real-world signals, such the one of an alto singer sustaining a steady note partially shown in Fig. \ref{fig:AnalyticSignalAlto}, the Hilbert transform alone provides a poor envelope, since it retains most of the frequencies of the underlying wave. With further processing, such as filtering, a smoother output can be obtained.

@@

The $ \odot $ operator in Equation \ref{eq:Envelope} stands for the Hadamard product and denotes element-wise multiplication of two vectors. Fig. \ref{fig:Envelope} provides an example of the vectors just defined: \textbf{w} is obtained by element-wise multiplication between the carrier wave \textbf{c} and the envelope \textbf{e}.

@@

Fig. \ref{fig:Envelope} helps to illustrate a key concept: only at some local extrema the envelope can be inferred without prior knowledge of the underlying carrier.

@@

The radius $ r_k $ of the circle equivalent to each $ v_k $ is defined in Equation \ref{eq:Radius}. This equation has the desirable property $ v_{k,y} \to 0 \implies v_{k,y} \to \infty $, that is, the radius tends to infinity when there is no vertical displacement, effectively turning the circle into a line.

@@

An example of such behaviour can be observed in Fig. \ref{fig:Comparison_sinusoid}, where the envelope of a simple sinusoid is shown. To see that this is always the case, note that all the extrema of a sinusoid are of the form $ a (\pm 1) $ and $ P_j = (i_j, \lvert a (\pm 1) \lvert) = (i_j, a) \ \forall P_j \in \text{P} $ in the original coordinate system. As $ \text{E} \subset \text{P} $, we have that the envelope $ \mathbf{e} = (a, a, \cdots, a) $ and is, thus, constant. Likewise, since $ \mathbf{w} = \mathbf{e} \odot \mathbf{c} $, we have $ c_i = a \cos(\omega i + \phi) / a = \cos(\omega i + \phi) \ \forall \ i, 0 \le i \le n - 1 $.

@@

\subsection{Reference envelope}

% In order to obtain a numeric indicator of the quality of an envelope, we construct a reference envelope, 
In \cite{1992BruceCurves,2019Jiaempirical}, the envelope is defined as the boundary of the region filled by a family of curves. Fig. \ref{fig:RefEnvelopeTheory} illustrates this concept, for a family of sinusoids that share the same frequency and amplitude, and whose phases vary from 0 to $ 2 \pi $.

@@

In practical applications, one seldom has access to a family of curves, instead being interested in obtaining the envelope of a single signal. Nevertheless, an approximation can be obtained, by shifting the original signal along its initial position in the horizontal axis by half of its period, and taking the absolute maximum value at each index $i$.
Fig. \ref{fig:RefEnvelope} shows part of the reference envelope for the sound of a tom drum.

@@

Although lacking in applicability, both given its discontinuous shape and the high computational cost, an envelope constructed in this way arises from a mathematically sound background, and can serve as a reference to infer the quality of more practical methods.

@@

Direct comparison with many recent algorithms is made difficult by the unavailability of digital implementations of such works, some of whice where designed to process analog signals \cite[e.g.][]{2018AssefModeling}.

>>>>

%%%%%%%%%%%%%%%%%%%%% TODO
As seen, the intuitive definition of an envelope describes it as a smooth curve; this smoothness requirement implies that the envelope should ideally be comprised of lower frequencies than the original signal.
For real-world signals, such as the one of an alto singer sustaining a steady note, partially shown in Fig. \ref{fig:AnalyticSignalAlto}, the Hilbert transform alone provides a poor envelope, since it retains most of the frequencies of the underlying wave.

Applying a low pass filter, we can coerce the result of the Hilbert transform to comply with the smoothness requirement, by removing high frequencies from the original result. This will potentially lead to undershoots, proportional to the initial high frequency content of the transform removed without compensation.
%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%% TODO
The $ \odot $ operator in Equation \ref{eq:Envelope} stands for the Hadamard product and denotes element-wise multiplication of two vectors. Fig. \ref{fig:Envelope} provides an example of the vectors just defined: \textbf{w} is obtained by element-wise multiplication between the carrier wave \textbf{c} and the envelope \textbf{e}.

Equation \ref{eq:Envelope} connects the three vectors \textbf{e}, \textbf{w} and \textbf{c} in the sense that each one can be derived from the other two. In most real world scenarios, however, only the original signal \textbf{w} is known, and the envelope \textbf{e} is to be retrieved without a priori knowledge of the carrier wave \textbf{c}.
%%%%%%%%%%%%%%%%%%%%%

@@

In this context, Fig. \ref{fig:Envelope} helps to illustrate a key concept: only at some local extrema the envelope can be inferred without prior knowledge of the underlying carrier.

@@

The radius $ r_k $ of the circle equivalent to each $ v_k $ is defined in Equation \ref{eq:Radius}. This equation has the desirable property $ v_{k,y} \to 0 \implies r_k \to \infty $, that is, the radius tends to infinity when there is no vertical displacement, effectively turning the circle into a line.

@@

An example of such behaviour can be observed in Section \ref{sec:comparison}, Fig. \ref{fig:Comparison_sinusoid}, where the envelope of a simple sinusoid is shown. To see that this is always the case, note that all the extrema of a sinusoid are of the form $ a (\pm 1) $ and $ P_j = (i_j, \lvert a (\pm 1) \lvert) = (i_j, a) \ \forall P_j \in \text{P} $ in the original coordinate system. As $ \text{E} \subset \text{P} $, we have that the envelope $ \mathbf{e} = (a, a, \cdots, a) $ and is, thus, constant. Likewise, since $ \mathbf{w} = \mathbf{e} \odot \mathbf{c} $, we have $ c_i = a \cos(\omega i + \phi) / a = \cos(\omega i + \phi) \ \forall \ i, 0 \le i \le n - 1 $.

@@

\subsection{Reference envelope}
% In order to obtain a numeric indicator of the quality of an envelope, we construct a reference envelope, 
In \cite{1992BruceCurves,2019Jiaempirical}, the envelope is defined as the boundary of the region filled by a family of curves. Fig. \ref{fig:RefEnvelopeTheory} illustrates this concept, for a family of sinusoids that share the same frequency and amplitude, and whose phases vary from 0 to $ 2 \pi $.

@@

In practical applications, one is generally interested in obtaining the envelope of a single known signal, seldom having access to a family of curves. By shifting this signal along its initial position, an approximation to a family of curves can be obtained, however, that can be used to construct a reference envelope.

Given a discrete signal $ \mathbf{w} $, the reference envelope $ \mathbf{r} = (r_0, r_1, \cdots, r_{n-1}) $ is formalized in equation \ref{eq:referenceenvelope}, where $ f $ is the predominant frequency of the original signal, as obtained by the maximum argument of the DFT of the original signal, and $ t $ its predominant period. Moreover, the value of the original signal $ \mathbf{w} $ outside the interval $ 0 \le i < n $ is assumed to be zero.

\begin{align} \label{eq:referenceenvelope}
  \begin{split}
    f &= \text{argmax} \big( \mathcal{F} (\mathbf{w}) \big) \\
    t &= n / f \\
    r_i &= \max(w_{i - t/2}, w_{i - t/2 + 1}, w_{i - t/2 + 2}, \cdots, w_{i + t/2})
  \end{split}
\end{align}

% Given an arbitrary signal, one can use the FFT to obtain its predominant period. The reference envelope is obtained by gradually shifting the original signal from a lag of

% Nevertheless, ,  in the horizontal axis by half of its period, and taking the absolute maximum value at each index $i$.
% Fig. \ref{fig:RefEnvelope} shows part of the reference envelope for the sound of a tom drum.

@@

Although lacking in applicability, both given its discontinuous shape and the high computational cost of its estimation, an envelope constructed in this way arises from a mathematically sound background, and can serve as a reference to infer the quality of more practical methods. This envelope is used in the comparisons presented in Table \ref{table:Error_comparison}

@@

Direct comparison with many recent algorithms is made difficult by the unavailability of digital implementations of such works, some of which where designed to process analog signals \cite[e.g.][]{2018AssefModeling}.
